---
title: "Chapter 2"
author: "arash haratian"
date: "3/20/2021"
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(fig.width = 6, fig.asp = 0.618, fig.align = "center")
```


# The 10-armed testbed

```{r, message = FALSE}
source("./ten_armed_testbed.R")
```


## Figure 2.1: Reward distribution of each action

```{r fig2.1}
plot_fig2.1()
```

## Figure 2.2: Average performance of epsilon-greedy action-value methods

### Average reward

```{r fig2.2.1}
plot_fig2.2.1()
```

### Percentage of optimal action

```{r fig2.2.2}
plot_fig2.2.2()
```

## Figure 2.3: The effect of optimistic initial action-value estimates

```{r fig2.3}
plot_fig2.3()
```


## Figure 2.4: Average performance of UCB action selection

```{r fig2.4}
plot_fig2.4()
```


## Figure 2.5: Average performance of the gradient bandit algorithm

```{r fig2.5}
plot_fig2.5()
```


## Figure 2.6: A parameter study of the various bandit algorithms

```{r fig2.6}
plot_fig2.6()
```

