---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Reinforcement Learning: An Introduction, 2nd edition

<!-- badges: start -->
<!-- badges: end -->

The goal of this repo is to generate the examples and figures of Sutton & Barto's book [Reinforcement Learning: An Introduction (2nd Edition)](http://incompleteideas.net/book/the-book.html) in R.


## Prerequisites and How to Use

All codes are self-contained and in order to execute any of the code you need to install the [R](https://www.r-project.org/) and the following packages:

- [Tidyverse](https://github.com/tidyverse/tidyverse)
- [reshape2](https://cran.r-project.org/web/packages/reshape2/index.html)
- [patchwork](https://github.com/thomasp85/patchwork)
- [plotly](https://plotly.com/) (only for 3D plot in chapter 10)


You can check [my session info](#session-info) for more detail.


You can find the code usage examples in `.Rmd` files or in `.R` files.

## RMarkdown Outputs

- [**Chapter 1**](Chapter1/Chapter1.html)
- [**Chapter 2**](Chapter2/Chapter2.html)
- [**Chapter 3**](Chapter3/Chapter3.html)
- [**Chapter 4**](Chapter4/Chapter4.html)
- [**Chapter 5**](Chapter5/Chapter5.html)
- [**Chapter 6**](Chapter6/Chapter6.html)
- [**Chapter 7**](Chapter7/Chapter7.html)
- [**Chapter 8**](Chapter8/Chapter8.html)
- [**Chapter 9**](Chapter9/Chapter9.html)
- [**Chapter 10**](Chapter10/Chapter10.html)
- [**Chapter 11**](Chapter11/Chapter11.html)
- [**Chapter 12**](Chapter12/Chapter12.html)
- [**Chapter 13**](Chapter13/Chapter13.html)



## Session Info

```{r, message = FALSE, warning = FALSE}
library(tidyverse)
library(reshape2)
library(patchwork)
library(plotly)

sessioninfo::session_info()
```


## Contributing

Pull requests are welcome. For major changes, you may want to open an issue first to discuss what you would like to change.
If you want to add some missing figures or make any improvement, you are welcomed to make a pull request or open an issue.

