---
title: "Chapter 10"
author: "arash haratian"
date: "4/15/2021"
output: 
  html_document:
    toc: true
    toc_float: true
---


```{r setup, include = FALSE}
knitr::opts_chunk$set(fig.width = 7, fig.asp = 0.618, fig.align = "center")
```


# Mountain Car task

```{r, message = FALSE}
source("./mountain_car.R")
```


## Figure 10.1: The Mountain Car task and the cost-to-go function


### Interactive 3D plot

```{r fig10.1_3D, message = FALSE, warning = FALSE, out.width = "100%"}
plot_fig10.1(plot_heatmap = FALSE)
```

### Heatmap plot

```{r fig10.1_heatmap, fig.width = 12, message = FALSE}
plot_fig10.1(plot_heatmap = TRUE)
```



## Figure 10.2: Mountain Car learning curves for the semi-gradient Sarsa method with tile-coding

```{r fig10.2, results = "hide"}
plot_fig10.2()
```


## Figure 10.3: Performance of one-step vs 8-step semi-gradient Sarsa

```{r fig10.3, results = "hide"}
plot_fig10.3()
```



## Figure 10.4: Effect of the alpha and n on early performance of n-step semi-gradient Sarsa

```{r fig10.4, results = "hide"}
plot_fig10.4()
```



```{r, echo = FALSE}
rm(list = ls())
```


# An Access-Control queuing task

```{r, message = FALSE}
source("./queuing.R")
```

## Figure 10.5: The policy and value function found by differential semi-gradient one-step Sarsa


```{r fig10.5}
plot_fig10.5()
```
