---
title: "Chapter 12"
author: "arash haratian"
date: "4/22/2021"
output: 
  html_document:
    toc: true
    toc_float: true
---


```{r setup, include = FALSE}
knitr::opts_chunk$set(fig.width = 7, fig.asp = 0.618, fig.align = "center")
```


# Offline lambda-return

```{r, message = FALSE}
source("./offline_lambda_return_random_walk.R")
```


## Figure 12.3: Performance of the off-line lambda-return algorithm on 19-state Random walk

```{r fig12.3}
plot_fig12.3()
```


```{r, echo = FALSE}
rm(list = ls())
```


# TD(lambda) and true online TD(lambda)

```{r, message = FALSE}
source("./TD_lambda_true_online_TD_lambda_random_walk.R")
```


## Figure 12.6: Performance of TD(lambda) algorithm on 19-state Random walk

```{r fig12.6, warning = FALSE}
plot_fig12.6()
```


## Figure 12.8: Performance of online lambda-return algorithm on 19-state Random walk

```{r fig12.8}
plot_fig12.8()
```



```{r, echo = FALSE}
rm(list = ls())
```



# Sarsa(lambda)

```{r, message = FALSE}
source("./sarsa_lambda_mountain_car.R")
```


## Figure 12.10: Early performance on the Mountain Car task of Sarsa(lambda)

```{r fig12.10, results = "hide"}
plot_fig12.10()
```



## Figure 12.11: Summary comparison of Sarsa(lambda) algorithms on Mountain Car

```{r fig12.11, results = "hide", fig.width = 12}
plot_fig12.11()
```