---
title: "Chapter 5"
author: "arash haratian"
date: "3/29/2021"
output: 
  html_document:
    toc: true
    toc_float: true
---


```{r setup, include = FALSE}
knitr::opts_chunk$set(fig.width = 7, fig.asp = 0.618, fig.align = "center")
```


# Monte Carlo policy evaluation

```{r, message = FALSE}
source("./Monte_Carlo_policy_evaluation_blackjack.R")
```


## Figure 5.1: Approximate state-value functions for the blackjack policy that sticks only on 20 or 21

```{r fig5.1, fig.width = 12}
plot_fig5.1()
```


```{r, echo = FALSE}
rm(list = ls())
```


# Monte Carlo ES

```{r, message = FALSE}
source("./Monte_Carlo_ES.R")
```

## Figure 5.2: The optimal policy and state-value function for blackjack

```{r fig5.2, fig.width = 12}
plot_fig5.2()
```


```{r, echo = FALSE}
rm(list = ls())
```


# Monte Carlo off-policy


```{r, message = FALSE}
source("./MC_off_policy_blackjack.R")
```


## Figure 5.3: Weighted importance sampling

```{r fig5.3}
plot_fig5.3()
```


```{r, echo = FALSE}
rm(list = ls())
```


# Infinite variance

```{r, message = FALSE}
source("./InfinteVariance.R")
```


## Figure 5.4: Ordinary importance sampling produces surprisingly unstable estimates

```{r}
plot_fig5.4()
```

